Modeling the near-wake of a vertical-axis cross-flow turbine with 2-D and 3-D RANS

### 2016-03-19 paper.tex
Remove table footnotes

% Footnotes in tables
\usepackage{tablefootnote}

@@

\begin{table}
    \centering
    \begin{tabular}{c|c|c|c}
        Author & Turbulence modeling & Perf. val. & Wake val. \\ 
        \hline
        Alaimo et al.~\cite{Alaimo2015} & $k$--$\epsilon$ & N/A & N/A \\ 
        Marsh et al.~\cite{Marsh2015} & SST & \cite{Rawlings2008} & N/A \\ 
        Orlandi et al.~\cite{Orlandi2015} & SST & \cite{Akins1989,Mertens2003} & N/A \\ 
        Lam \& Peng~\cite{Lam2016} & SST RANS \& IDDES\tablefootnote{Improved delayed detached-eddy simulation.} & N/A & \cite{Tescione2014} \\ 
        Nini et al.~\cite{Nini2014} & Spalart--Allmaras & N/A & \cite{Battisti2011} \\ 
        Boudreau \& Dumas~\cite{Boudreau2015} & DDES\tablefootnote{Delayed detached-eddy simulation.} & N/A & N/A \\ 
        Li et al.~\cite{Li2013} & SST \& Smagorinsky--Lilly LES & \cite{McLaren2011} & N/A \\ 
        Howell et al.~\cite{Howell2010} & $k$--$\epsilon$ RNG\tablefootnote{Renormalization group.} & \cite{Howell2010} & N/A
    \end{tabular}

>>>>

@@

\begin{table}
    \centering
    \begin{tabular}{c|c|c|c}
        Author & Turbulence modeling & Perf. val. & Wake val. \\ 
        \hline
        Alaimo et al.~\cite{Alaimo2015} & $k$--$\epsilon$ & N/A & N/A \\ 
        Marsh et al.~\cite{Marsh2015} & SST & Reference~\cite{Rawlings2008} & N/A \\ 
        Orlandi et al.~\cite{Orlandi2015} & SST & References~\cite{Akins1989,Mertens2003} & N/A \\ 
        Lam \& Peng~\cite{Lam2016} & SST RANS \& IDDES & N/A & Reference~\cite{Tescione2014} \\ 
        Nini et al.~\cite{Nini2014} & Spalart--Allmaras & N/A & Reference~\cite{Battisti2011} \\ 
        Boudreau \& Dumas~\cite{Boudreau2015} & DDES & N/A & N/A \\ 
        Li et al.~\cite{Li2013} & SST \& Smagorinsky--Lilly LES & Reference~\cite{McLaren2011} & N/A \\ 
        Howell et al.~\cite{Howell2010} & $k$--$\epsilon$ RNG & Reference~\cite{Howell2010} & N/A
    \end{tabular}
